### 2022-01-13 input/experiments.tex
objective and description of expe, todo results

\begin{figure*}
  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
    comprising 40 interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet}.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  } \subfloat[PartB][\label{fig:xascast}
    \TODO{Experiment with ascast against xascast? with different cache
      size}]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
  }
  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
\end{figure*}

@@

@@

% \subsection{Use case: caching}
% \subsection{Use case: routing}
% \subsection{Use case: broadcast domain}

>>>>

\begin{figure*}
  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
    comprising 40 interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet}.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  } \subfloat[PartB][\label{fig:europe_as_vs_xas}
    \TODO{Experiment with ascast against xascast? with different cache
      size}]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
  }
  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
\end{figure*}

@@

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that fits this context by
    enabling lazy dynamic partitioning.

  \item[Description:] We build a network of networks by using an Edge
    infrastructure comprising 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet} as depicted in
    Figure~\ref{fig:europe-ases}. \emph{Gateway} \processes (dark in
    the figure) link autonomous systems together, \eg a Lisbon \node
    links Portugal to Spain and United Kingdoms through a Madrid \node
    and a London \node respectively.

    \noindent Figure~\ref{fig:europe-ases} depicts the operations executed
    during the simulation that lasts 7 seconds: at 1 second, a \node
    located in Lisbon, Portugal performs an \texttt{Add}; at 2
    seconds, a \node located in Palma de Majorque, Spain performs an
    \texttt{Add}; at 3 seconds, a \node located in Paris, France
    performs an \texttt{Add}; at 4 seconds, a \node located in
    Hvanneyri, Iceland performs an \texttt{Add}; and finally, at 5
    seconds, the \node in Spain performs a \texttt{Del}.

    \noindent \NAMEC extends \NAME to enable lazy dynamic partitioning
    by allowing gateways to stop notifications when their respective
    network does not appear to have a source. Using \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous systems, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie contiguous autonomous systems that have at least one
    source.

    \noindent We measure the number of messages transiting through the
    network for each operation, and we measure the number of
    \processes that index (\ie belong to a partition) over time.

  \item[Results:] Figure~\ref{fig:europe_as_vs_xas} shows the results
    of this experiment.
\end{asparadesc}

@@
